ZCB Pricing

### 2018-10-15 ZCB Pricing .Rmd
NEW MC

  #Simulate interest rates
  dt <- T/s # Length of sub-intervals
  sim_path = matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path[1,]= r # Initial rates on first row.

  for (i in 1:n){
    for (j in 2:(s+1)){
      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*rnorm(1)# Discretize the SDE of the interest model using Euler Discretization to simulate rates over discrete sub-intervals
      sim_path[j,i]=sim_path[j-1,i]+dr
    }
  }

@@

  for (i in 1:n){
    z = rnorm(1)# Generate standard normal values
    z.=-z
    for (j in 2:(s+1)){
      dr = (alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z # Same Euler Discretization as in the Crude Monte Carlo function
      dr_i = (alpha-beta*sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z. # Euler Discretization for the use of -Z_i
      sim_path[j,i] =sim_path[j-1,i]+dr
      sim_path_inv[j,i] = sim_path_inv[j-1,i]+dr_i

@@

  # Follow the same process as in the Monte Carlo approach , but use the transformed Z_i's to simulate the rates
  for (i in 1:n){
    for (j in 2:(s+1)){
      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z_m[i] 
      sim_path[j,i]=sim_path[j-1,i]+dr
    }
  }

@@

  dt <- T/s # Length of sub-intervals
  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path[1,]= r

  for (i in 1:n){
    for (j in 2:(s+1)){
      dr=(alpha-beta*sim_path[j-1,i])*dt+(sigma*sqrt(dt)*rnorm(1)*sqrt(sim_path[j-1,i]))# Euler Discretization
      sim_path[j,i]=sim_path[j-1,i]+dr

>>>>

  #Simulate interest rates
  dt <- T/s # Length of sub-intervals
  sim_path = matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path[1,]= r # Initial rates on first row.
  z = rnorm(n)

  for (i in 1:n){
    for (j in 2:(s+1)){
      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[j]# Discretize the SDE of the interest model using Euler Discretization to simulate rates over discrete sub-intervals
      sim_path[j,i]=sim_path[j-1,i]+dr
    }
  }

@@

    z = rnorm(n)# Generate standard normal values
    z.=-z

  for (i in 1:n){

    for (j in 2:(s+1)){
      dr = (alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[j] # Same Euler Discretization as in the Crude Monte Carlo function
      dr_i = (alpha-beta*sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z.[j] # Euler Discretization for the use of -Z_i
      sim_path[j,i] =sim_path[j-1,i]+dr
      sim_path_inv[j,i] = sim_path_inv[j-1,i]+dr_i

@@

  # Follow the same process as in the Monte Carlo approach , but use the transformed Z_i's to simulate the rates
  for (i in 1:n){
    for (j in 2:(s+1)){
      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z_m[j] 
      sim_path[j,i]=sim_path[j-1,i]+dr
    }
  }

@@

  dt <- T/s # Length of sub-intervals
  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path[1,]= r
  z <- rnorm(n)

  for (i in 1:n){
    for (j in 2:(s+1)){
      dr=(alpha-beta*sim_path[j-1,i])*dt+(sigma*sqrt(dt)*z[j]*sqrt(sim_path[j-1,i]))# Euler Discretization
      sim_path[j,i]=sim_path[j-1,i]+dr
